Business Analytics 1 : Finding Groups Within the Data

### 2016-02-15 1_finding_groups/finding_groups.Rmd
add sources
new readme

> This documentation assumes you're familiar with R and hierarchical clustering, thus technical details are not explained.

@@

- **volaility** : This can be measured by the [coefficient of variation](https://en.wikipedia.org/wiki/Coefficient_of_variation), which is simply the standard deviation of sales divided by the mean sales for each SKU.

@@

## Takeaways

1. There are different perspective (intuition, business sense, technical approaches) as to which variable should have or should not have been included in the dataset prior to running the clustering method. As clustering algorithms are so categorized under unsupervised algorithms, there're really no "correct" ouput, so choose your variables or features wisely ! Suppose that for some reason you think that it's nonsense to exclude the `S` variable : the satisfaction level, like we did in this documentation, you should add it back and run the clustering, though you'll obtain similar grouping results for this dataset, and when you realize that whether you include a variable or not does not affect the result, you should exclude it as this lessen the calculation loading for the algorithm and your computer.

2. After you obtain the results, giving visualizations and naming your segmentations in a self explanatory and meaningful way can make your results more convincing. We've heard like a billion times already that a picture is worth thousands of words. And more importantly, you should always ask yourself, given the results what are you going to do with it, how can this result help my business goals ?

@@

>>>>

> This documentation assumes you're familiar with hierarchical clustering.

@@

- **volatility** : This can be measured by the [coefficient of variation](https://en.wikipedia.org/wiki/Coefficient_of_variation), which is simply the standard deviation of sales divided by the mean sales for each SKU.

@@

**Takeaways:**

1. There are different perspective (intuition, business sense, technical approaches) as to which variable should have or should not have been included in the dataset prior to running the clustering method. As clustering algorithms are categorized under unsupervised algorithms, meaning that there is no way of measuring whether the ouput is "correct". Thus you should choose your input variables (features) wisely! Speaking of this, suppose that for some reason you think that it's nonsense to exclude the `S` variable : the satisfaction level, like we did in this documentation. You should add it back and run the clustering, though you'll obtain similar grouping results for this dataset, and when you realize that whether you included a variable or not does not affect the result, you should exclude it as this lessen the calculation loading for the algorithm and your computer.

2. After you obtain the results, giving visualizations and naming your segmentations in a self explanatory and meaningful way can make your results more convincing. We've heard like a billion times already that a picture is worth thousands of words. And more importantly, you should always ask yourself, given the results what are you going to do with it, how can this result help my business goals?

@@

**Sources:**
